Supplementary Information

### 2016-09-01 supplementary/supplementary.tex
new pdf

@@

\title{Supplementary Information}

@@

\begin{algorithm}[!t]   \caption{Alternating Least Squares}
   \label{alg}
   %\begin{minipage}{0.9\textwidth}
   \begin{small}
\begin{algorithmic}[1]
\STATE \textbf{Input}: \\
$k$ : number of latent factors\\
$\Gamma$: pairs of entities for initialization\\
For every task $t$,\\
${\{\mathbf{x}_{ti}\}, \{\mathbf{y}_{tj}\}}$: feature vectors for pathogen and host proteins resp.\\
$\Omega_t$: the observed entries of the matrix $M_t$\\
\STATE \textbf{Initialization}: \\
\STATE An iteration $r$, let $\mathbf{S}^r$ represent $\{S^r_t\}_{t=1}^T$
\STATE $\mathbf{S}^0 \leftarrow 0$
\STATE $U^0 \leftarrow$ top-$k$ left singular vectors and $V^0 \leftarrow$ top-$k$ right singular vectors from the SVD of $\displaystyle{\sum_{(i,j) \in \Gamma}} \mathbf{x}_i \mathbf{y}_j^\intercal$\\
\STATE $\mathcal{L}^0$ : initial loss
\REPEAT
  \STATE $U^{r+1} \leftarrow \displaystyle{\argmin_{U}} \; \mathcal{L}(U, V^r, \mathbf{S}^r)$  \STATE $V^{r+1} \leftarrow \displaystyle{\argmin_{V}} \; \mathcal{L}(U^{r+1}, V, \mathbf{S}^r) $  \STATE For each task $t$\\
  \hspace{0.5cm} $S^{r+1}_t \leftarrow \displaystyle{\argmin_{S_t}} \; \mathcal{L}(U^{r+1}, V^{r+1}, \mathbf{S}^r_{-t}) $
  \STATE Compute $\mathcal{L}^{r+1}$ and let $\delta \leftarrow (\mathcal{L}^r - \mathcal{L}^{r+1})/\mathcal{L}^r$
\UNTIL {$\delta < \tau$}%\While
\end{algorithmic}\end{small}
%\end{minipage}
\end{algorithm}

@@

\begin{figure}[h]
\begin{floatrow}
\ffigbox[0.3\columnwidth]{%
%trim option's parameter order: left bottom right top
\includegraphics[scale=0.25, trim = 0.2cm 0 0 0]{fig7-eps-converted-to.pdf}
}{%
\caption{Sequence motif from top four-mer features specific to \textit{Ebola} proteins}%
\label{fig:ebola_motifs}
}

\ffigbox[0.3\columnwidth]{%
%trim option's parameter order: left bottom right top
\includegraphics[scale=0.25, trim = 0 0 0 0]{fig8-eps-converted-to.pdf}
}{%
\caption{Sequence motifs specific to \textit{Hepatitic-C} proteins that are also important to interactions.}%
\label{fig:hepc_motifs}
}

\ffigbox[0.3\columnwidth]{%
%trim option's parameter order: left bottom right top
\includegraphics[scale=0.25, trim = 0 0 0 0]{fig9-eps-converted-to.pdf}
}{%
\caption{Sequence motifs specific to \textit{Influenza} proteins that are also important to interactions.}%
\label{fig:flu_motifs}
}

@@

\begin{figure}[h]
\begin{floatrow}
\ffigbox[0.4\columnwidth]{%
%trim option's parameter order: left bottom right top
\includegraphics[scale=0.25, trim = 0 0 0 0]{top10ebola_3mers_seq2logo.pdf}
}{%
\caption{Sequence motifs specific to \textit{Ebola} proteins that are also important to interactions.}%
\label{fig:hepc_motifs}
}

\ffigbox[0.4\columnwidth]{%
%trim option's parameter order: left bottom right top
\includegraphics[scale=0.25, trim = 0 0 0 0]{top10flavi_3mers_seq2logo.pdf}
}{%
\caption{Sequence motifs specific to \textit{Hepatitic-C} proteins that are also important to interactions.}%
\label{fig:hepc_motifs}
}
\end{floatrow}
\end{figure}

\begin{figure}[h]
\begin{floatrow}
\ffigbox[0.4\columnwidth]{%
%trim option's parameter order: left bottom right top
\includegraphics[scale=0.25, trim = 0 0 0 0]{top10flu_3mers_seq2logo.pdf}
}{%
\caption{Sequence motifs specific to \textit{Influenza} proteins that are also important to interactions.}%
\label{fig:flu_motifs}
}
\ffigbox[0.4\columnwidth]{%
%trim option's parameter order: left bottom right top
\includegraphics[scale=0.25, trim = 0 0 0 0]{top10human_3mers_seq2logo.pdf}
}{%
\caption{Sequence motif constructed from the top tri-mer features of human proteins}%
\label{fig:human_motifs}
}
\end{floatrow}
\end{figure}

\bibliographystyle{plain}
\bibliography{references}

>>>>

\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}

@@

\noindent{\Huge Supplementary Information}

@@

\begin{algorithm}[!h]   \caption{Alternating Least Squares}
   \label{alg}
   %\begin{minipage}{0.9\textwidth}
   \begin{small}
\begin{algorithmic}[1]
\STATE \textbf{Input}: \\
$k$ : number of latent factors\\
$\Gamma$: pairs of entities for initialization\\
For every task $t$,\\
${\{\mathbf{x}_{ti}\}, \{\mathbf{y}_{tj}\}}$: feature vectors for pathogen and host proteins resp.\\
$\Omega_t$: the observed entries of the matrix $M_t$\\
\STATE \textbf{Initialization}: \\
\STATE An iteration $r$, let $\mathbf{S}^r$ represent $\{S^r_t\}_{t=1}^T$
\STATE $\mathbf{S}^0 \leftarrow 0$
\STATE $U^0 \leftarrow$ top-$k$ left singular vectors and $V^0 \leftarrow$ top-$k$ right singular vectors from the SVD of $\displaystyle{\sum_{(i,j) \in \Gamma}} \mathbf{x}_i \mathbf{y}_j^\intercal$\\
\STATE $\mathcal{L}^0$ : initial loss
\REPEAT
  \STATE $U^{r+1} \leftarrow \displaystyle{\argmin_{U}} \; \mathcal{L}(U, V^r, \mathbf{S}^r)$  \STATE $V^{r+1} \leftarrow \displaystyle{\argmin_{V}} \; \mathcal{L}(U^{r+1}, V, \mathbf{S}^r) $  \STATE For each task $t$\\
  \hspace{0.5cm} $S^{r+1}_t \leftarrow \displaystyle{\argmin_{S_t}} \; \mathcal{L}(U^{r+1}, V^{r+1}, \mathbf{S}^r_{-t}) $
  \STATE Compute $\mathcal{L}^{r+1}$ and let $\delta \leftarrow (\mathcal{L}^r - \mathcal{L}^{r+1})/\mathcal{L}^r$
\UNTIL {$\delta < \tau$}%\While
\end{algorithmic}\end{small}
%\end{minipage}
\end{algorithm}

@@

\begin{figure}[h]
\begin{floatrow}
\ffigbox[0.45\columnwidth]{%
%trim option's parameter order: left bottom right top
\includegraphics[scale=0.25, trim = 0.2cm 0 0 0]{fig7-eps-converted-to.pdf}
}{%
\caption{Sequence motif from top four-mer features specific to \textit{Ebola} proteins}%
\label{fig:ebola_motifs}
}

\ffigbox[0.45\columnwidth]{%
%trim option's parameter order: left bottom right top
\includegraphics[scale=0.25, trim = 0 0 0 0]{fig9-eps-converted-to.pdf}
}{%
\caption{Sequence motifs specific to \textit{Influenza} proteins that are also important to interactions.}%
\label{fig:flu_motifs}
}

@@

\begin{figure}[h]
\begin{floatrow}
\ffigbox[0.45\columnwidth]{%
%trim option's parameter order: left bottom right top
\includegraphics[scale=0.25, trim = 0 0 0 0]{top10flavi_3mers_seq2logo.pdf}
}{%
\caption{Sequence motifs specific to \textit{Hepatitic-C} proteins that are also important to interactions.}%
\label{fig:hepc_motifs}
}
\ffigbox[0.45\columnwidth]{%
%trim option's parameter order: left bottom right top
\includegraphics[scale=0.25, trim = 0 0 0 0]{top10human_3mers_seq2logo.pdf}
}{%
\caption{Sequence motif constructed from the top tri-mer features of human proteins}%
\label{fig:human_motifs}
}
\end{floatrow}
\end{figure}

%\bibliographystyle{plain}
%\bibliography{references}
